### 2015-07-13 fundamentals/examples.tex
reviewer 2: page 20: bad reference for:  Section ??
fixes #121 according to suggestion given by @gidden"

\subsection{Simulations}
\label{ref:simulation}
%Inpro example (is this still running or did we deprecate it with 1.0?)

@@

This section will discuss the creation and results of a few simple fuel cycle
simulations to help illustrate the flexibility of \Cyclus. These simulations are
designed to illustrate Cyclus' capability.  Many simplifying assumptions have
been made with respect to material compositions, fuel transmutation, among
others. The three fuel cycles examined are:

>>>>

\subsection{Simulations}
\label{ref:simulations}
%Inpro example (is this still running or did we deprecate it with 1.0?)

@@

This section will discuss the creation and results of a few simple fuel cycle
simulations to help illustrate the flexibility of \Cyclus. These examples are
not the limit of \Cyclus' capabilities, which are extended with each new
addition to the ecosystem, as discussed above.  Rather, these simulations are
designed to illustrate that \Cyclus has capabilities matching those of any
recipe-based simulator.  Accordingly, many simplifying assumptions have been
made with respect to material compositions, fuel transmutation, among others.
The three fuel cycles examined are:
